The Next Release Problem in Real World

### 2018-12-18 PaperBody.tex
conclusion
Conclusion
Updates from ShareLaTeX

https://github.com/shkevinlee/CS454

@@

%At first experiment, we applied five algorithms to four datasets and compared the maximum profit each other. In \textbf{Table \ref{table:DatasetProfit}}, upper two rows are estimated cost sum and real profit sum of each datasets. Below these rows, there are averaged profits for each algorithms on four datasets. At the result, every profits for algorithms are bigger than real profit sum. Also, consumed time to return maximum profit was exceedingly short in ILP and AHP, rather than SA, GA, and NSGA-II.

%\textbf{Figure \ref{fig:DatasetProfit}} is the graphs of \textbf{table 1}. Each graph %expresses the averaged profit of five algorithms. At the result, the profit of ILP is %the biggest, and the profit of NSGA-II and AHP is bigger than SA and GA in most case. %Except ILP and AHP, maximum profit is high in order of NSGA-II, GA, then SA.

%At experiment 2, we got the profits while changing the cost constraint. The result is expressed in \textbf{Figure \ref{fig:paretofronts}}. \textbf{Figure \ref{fig:paretofronts}} expresses maximum profits on each cost, and \textbf{Figure 3} is integrating graph of \textbf{Figure 2} because of comparing the difference for four algorithms.

%The result is that they are all increasing almost similarly. One of the reasons to perform this experiment was that we wondered if there is a peculiar part in cost-profit graph.(if there is exceeding increase in profit) And at the result, there is no prominently peculiar part, and all the results are increasing normally.

@@

@@

In the results of the experiment.
EX1. was profit comparison. Exept for dataset with priority, the ILP has the highest result. And deterministic algorithms that AHP and ILP are very fast than heuristic algorithms. Ex2. is a comparison of the results of the profit according to the cost limit. As we mentioned, we found that limits of the Cost and the Profit had a linear relationship, regardless of algorithm. These results show that tere are no major problems with applying NRP argorithms to our dataset. Therefore, the dataset was well set to solve  the NRP.

>>>>

https://github.com/shkevinlee/CS454 \\ and the brief test implementation is described in \textbf{Test.py} in there.

@@

@@

\begin{figure*}[h]
\centering
  \begin{subfigure}[b]{0.95\linewidth}
    \includegraphics[width=\linewidth]{images/heatmap_ec.png}
  \end{subfigure}
  \caption{EX3-Requirements Heatmap in Eclipse Repositories(white = selected, Black = unselected)}
  \label{fig:EclipseHeatmap}
\end{figure*}

@@

In the results of the experiment.
EX1. was profit comparison. Exept for dataset with priority, the ILP has the highest result. And deterministic algorithms that AHP and ILP are very fast than heuristic algorithms. And Ex1 can answer RQ3 and RQ4. Ex2. is a comparison of the results of the profit according to the cost limit. As we mentioned, we found that limits of the Cost and the Profit had a linear relationship, regardless of algorithm. but it doesn't seem have much meaning. In RQ6. The result of algorithms were similar to those actual selection. These results show that tere are no major problems with applying NRP argorithms to our dataset. Therefore, the dataset was well set to solve the NRP.
